---
title: "Penguins ANOVA"
author: "Juan Espinoza"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. load packages and read-in penguins.csv data

```{r, include=FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

our question is there a significance difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie)?

2. Do some exploring

new functions: with + table for easy counting over multiple factos

update the speces name using case_when


```{r}
counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>%
  mutate(common_name =
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

```


Exploratory Graphs
Summary statistics
Levene's test for equal variances
one-way ANOVA
post-hoc testing


```{r}

hist <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~ common_name)

hist

qqs <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~ common_name)

qqs



# Levene's test for equal variances (> 2 groups...if you have two groups, use the F-test for equal variances)

# We'll use the function leveneTest from the 'car' package

#H0: Variances are equal
#HA: Variances are unequal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)

penguin_levene

# We retain the null hypothesis of equal variances (p = 0.06)

variances <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )

variances

```

#3 one-way ANOVA 

single factor: common name (species)
number of levels in the factor: 3 (chinstrap, gentoo, adelie)
random variable: flipper_length (mm)

Is there a significant difference in mean flipper length (mm) for female chinstrap, gentoo, and adelie penguins


```{r}
# H0: Mean flipper lengths across all species are equal
# HA: At LEAST two means differ significantly

penguin_aov <- aov(flipper_length ~ common_name, data = penguins2)

summary(penguin_aov)

# At least two samples were taken from populations with different means. which ones are different? all three are different from each other? or something else?

# There a significant difference between flipper length between species

# mean flipper lengths for adelie, gentoo, and chinstrap penguins are significantly different (f(df) = statistic, p < 0.001, $\alpha$ = 0.05 with post-hoc Tukey HSD, $\alpha$ = 0.05.

# Post-hoc testing using tukey's HSD

penguin_ph <- TukeyHSD(penguin_aov)
penguin_ph
```

